Number recognition for use in a Sudoku solver

### 2012-03-15 doc/icml2010stylefiles/paper.tex
abstract

\begin{abstract}
ICML 2010 full paper submissions are due February 1, 2010. Reviewing will
be blind to the identities of the authors, and therefore identifying
information should not appear in any way in papers submitted for
review. Submissions must be in PDF, 8 page length limit.
\end{abstract}

>>>>

\begin{abstract}
The goal of this work is to implement number recognition for a Soduko solver.
First we will describe the generation of synthetic data, in this case labelled images of numbers.
Then we compare different machine learning techniques for supervised learning using the generated data.
Once the training is complete, images of real Sudokus are captured using the webcam.
The different methods then try to correctly predict each number.
\end{abstract}
